---
title: "Lecture 13 Example Code"
author: "Christopher Prener, Ph.D."
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

## Introduction
This notebook illustrates code for working with multiple regression models.

## Dependencies
This notebook requires the `stats` package from base `R` as well as:

```{r load-packages}
# tidyverse packages
library(dplyr)         # data wrangling
library(ggplot2)       # plotting data

# other packages
library(here)          # file path management
library(stargazer)     # tables
```

## Load Data
This notebook requires the `mpg` data from `ggplot2`:

```{r load-data}
autoData <- mpg
```

## Data Preparation
We want to create a `foreign` variable:

```{r clean-data}
autoData %>%
  mutate(foreign = ifelse(manufacturer == "audi" | manufacturer == "honda" | manufacturer == "hyundai" | 
                            manufacturer == "land rover" | manufacturer == "nissan" | manufacturer == "subaru" |
                            manufacturer == "toyota" | manufacturer == "volkswagen", TRUE, FALSE)) -> autoData
```


## Fitting OLS Models
Models should be fit in stages and their results stored in separate objects. First, we'll fit our so-called "main effect" model:

```{r fit-models}
model1 <- lm(hwy ~ foreign, data = autoData)
```

The results are stored in a list named `model1` that can be visually inspected by clicking on the object in the Enviornment pane.

We can programatically access aspects of the model with dedicated functions `base::summary()` and `stats::confint()`:

```{r model1-summary}
summary(model1)
```

The `summary()` output includes the betas, r-squared, the root mean squared error, and the f-statistic.

We can also access the conifdence intervals:

```{r model1-ci}
confint(model1)
```

Finally, we can use `stats::AIC()` and `stats::BIC()` to access model fit statistics. We want to make sure we use `round()` to limit their output.

```{r model1-fit}
aic1 <- round(AIC(model1), digits = 3)
bic1 <- round(BIC(model1), digits = 3)
```

We'll fit a second model that controls for various measures of how fuel efficient the car is:

```{r model2}
model2 <- lm(hwy ~ foreign+displ+cyl+cty, data = autoData)
aic2 <- round(AIC(model2), digits = 3)
bic2 <- round(BIC(model2), digits = 3)
```

## Regression Tables
We can use `stargazer` to produce a publication-ready table in `html` that can be imported into Microsoft Word:

```{r model-table}
stargazer(model1, model2,
  title = "Regression Results",
  add.lines = list(c("AIC", aic1, aic2),c("BIC", bic1, bic2)), 
  omit.stat = "rsq", df = FALSE, 
  type = "html", out = here("extras", "models.html"))
```

## Descriptive Statistics Tables
We can also create a replacement for the handout's descriptive statistics table:

```{r descriptives-table}
autoData %>%
  select(hwy, foreign, displ, cyl, cty) -> autoSub

stargazer(data.frame(autoSub), 
  title = "Descriptive Statistics",
  summary = TRUE, omit.summary.stat = c("p25", "p75"),
  type = "html", out = here("extras", "descriptives.html"))
```

